Supporting Information

### 2018-04-23 SupportingInformation.Rmd
error bar plot fixing

<!--Shya to implement the modelling we discussed on 2018 04 12 and make results appear here!-->
```{r cause4copula_pGOF_500, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed=101)
#---------------------------------------
pdf("./Results/Cause4copula_results/compare_params_pGOF_num_keep_last_500.pdf", width=12, height=6)
op<-par(mfrow=c(2,4),mar=c(3,3.5,3,3.5), mgp=c(1.5,0.5,0))

Plotter_Cause4copula_GOF(N=5000,fcode=3,method = "spearman",num_keep_last=500,BS=1000)
Plotter_Cause4copula_GOF(N=5000,fcode=13,method="spearman",num_keep_last=500,BS=1000)
Plotter_Cause4copula_GOF(N=5000,fcode=4,method = "spearman",num_keep_last=500,BS=1000)
Plotter_Cause4copula_GOF(N=5000,fcode=14,method="spearman",num_keep_last=500,BS=1000)

Plotter_Cause4copula_GOF(N=5000,fcode=3,method = "kendall",num_keep_last=500,BS=1000)
Plotter_Cause4copula_GOF(N=5000,fcode=13,method="kendall",num_keep_last=500,BS=1000)
Plotter_Cause4copula_GOF(N=5000,fcode=4,method = "kendall",num_keep_last=500,BS=1000)
Plotter_Cause4copula_GOF(N=5000,fcode=14,method="kendall",num_keep_last=500,BS=1000)

@@

op<-par(fig = c(0, 1, 0, 1), oma = c(0, 0, 0, 0), mar = c(0, 0, 0, 0), new = TRUE)
plot(0, 0, type = "n", bty = "n", xaxt = "n", yaxt = "n")
legend("top", c("noise","population", "p_CvM", "p_KS"), col = c("red", "blue", "magenta", "green2"),
       cex = 1.5, pch = c(2, 6, 16, 16), lty = c(1, 1, NA, NA), xpd = TRUE, horiz = TRUE, inset = c(0,0), 
       bty = "n") 
par(op)
dev.off()
```

```{r cause4copula_pGOF_2500, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed=101)
#---------------------------------------
# I need to fix that SG_kendall ylimit error : I think I fixed it
#----------------------------
pdf("./Results/Cause4copula_results/compare_params_pGOF_num_keep_last_2500.pdf", width=12, height=6)
op<-par(mfrow=c(2,4),mar=c(3,3.5,3,3.5), mgp=c(1.5,0.5,0))

Plotter_Cause4copula_GOF(N=5000,fcode=3,method = "spearman",num_keep_last=2500,BS=1000)
Plotter_Cause4copula_GOF(N=5000,fcode=13,method="spearman",num_keep_last=2500,BS=1000)
Plotter_Cause4copula_GOF(N=5000,fcode=4,method = "spearman",num_keep_last=2500,BS=1000)
Plotter_Cause4copula_GOF(N=5000,fcode=14,method="spearman",num_keep_last=2500,BS=1000)

Plotter_Cause4copula_GOF(N=5000,fcode=3,method = "kendall",num_keep_last=2500,BS=1000)
Plotter_Cause4copula_GOF(N=5000,fcode=13,method="kendall",num_keep_last=2500,BS=1000)
Plotter_Cause4copula_GOF(N=5000,fcode=4,method = "kendall",num_keep_last=2500,BS=1000)
Plotter_Cause4copula_GOF(N=5000,fcode=14,method="kendall",num_keep_last=2500,BS=1000)

op<-par(fig = c(0, 1, 0, 1), oma = c(0, 0, 0, 0), mar = c(0, 0, 0, 0), new = TRUE)
plot(0, 0, type = "n", bty = "n", xaxt = "n", yaxt = "n")
legend("top", c("noise","population", "p_CvM", "p_KS"), col = c("red", "blue", "magenta", "green2"),
       cex = 1.5, pch = c(2, 6, 16, 16), lty = c(1, 1, NA, NA), xpd = TRUE, horiz = TRUE, inset = c(0,0), 
       bty = "n") 
par(op)
dev.off()
```

>>>>

<!--Shya to implement the modelling we discussed on 2018 04 12 and make results appear here!-->
```{r cause4copula_pGOF_500, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed=101)
#---------------------------------------
pdf("./Results/Cause4copula_results/compare_params_pGOF_num_keep_last_500.pdf", width=8, height=6)
op<-par(mfrow=c(2,2))

Plotter_Cause4copula_GOF(N=5000,fcode=3,method = "spearman",num_keep_last=500,BS=1000)
Plotter_Cause4copula_GOF(N=5000,fcode=13,method="spearman",num_keep_last=500,BS=1000)
#Plotter_Cause4copula_GOF(N=5000,fcode=4,method = "spearman",num_keep_last=500,BS=1000)
#Plotter_Cause4copula_GOF(N=5000,fcode=14,method="spearman",num_keep_last=500,BS=1000)

Plotter_Cause4copula_GOF(N=5000,fcode=3,method = "kendall",num_keep_last=500,BS=1000)
Plotter_Cause4copula_GOF(N=5000,fcode=13,method="kendall",num_keep_last=500,BS=1000)
#Plotter_Cause4copula_GOF(N=5000,fcode=4,method = "kendall",num_keep_last=500,BS=1000)
#Plotter_Cause4copula_GOF(N=5000,fcode=14,method="kendall",num_keep_last=500,BS=1000)

@@

op<-par(fig = c(0, 1, 0, 1), oma = c(0, 0, 0, 0), mar = c(0, 1, 0, 0), new = TRUE)
plot(0, 0, type = "n", bty = "n", xaxt = "n", yaxt = "n")
legend("top", c("noise", "population", "p_CvM", "p_KS"), col = c("red", "blue", "magenta", "green2"),
       cex = 1.5, pch = c(2, 6, 16, 16), xpd = TRUE, horiz = TRUE, inset = c(0,0), 
       bty = "n") 
par(op)
dev.off()
```

```{r cause4copula_pGOF_2500, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed=101)
#---------------------------------------
# I need to fix that SG_kendall ylimit error : I think I fixed it
#----------------------------
pdf("./Results/Cause4copula_results/compare_params_pGOF_num_keep_last_2500.pdf", width=8, height=6)
op<-par(mfrow=c(2,2))

Plotter_Cause4copula_GOF(N=5000,fcode=3,method = "spearman",num_keep_last=2500,BS=1000)
Plotter_Cause4copula_GOF(N=5000,fcode=13,method="spearman",num_keep_last=2500,BS=1000)
#Plotter_Cause4copula_GOF(N=5000,fcode=4,method = "spearman",num_keep_last=2500,BS=1000)
#Plotter_Cause4copula_GOF(N=5000,fcode=14,method="spearman",num_keep_last=2500,BS=1000)

Plotter_Cause4copula_GOF(N=5000,fcode=3,method = "kendall",num_keep_last=2500,BS=1000)
Plotter_Cause4copula_GOF(N=5000,fcode=13,method="kendall",num_keep_last=2500,BS=1000)
#Plotter_Cause4copula_GOF(N=5000,fcode=4,method = "kendall",num_keep_last=2500,BS=1000)
#Plotter_Cause4copula_GOF(N=5000,fcode=14,method="kendall",num_keep_last=2500,BS=1000)

op<-par(fig = c(0, 1, 0, 1), oma = c(0, 0, 0, 0), mar = c(0, 0, 0, 0), new = TRUE)
plot(0, 0, type = "n", bty = "n", xaxt = "n", yaxt = "n")
legend("top", c("noise", "population", "p_CvM", "p_KS"), col = c("red", "blue", "magenta", "green2"),
       cex = 1.5, pch = c(2, 6, 16, 16), xpd = TRUE, horiz = TRUE, inset = c(0,0), 
       bty = "n") 
par(op)
dev.off()
```
